\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2012-10-26 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
updates the user manual; modifies all parameter files

@@

@@

\item [{\texttt{HDUR\_MOVIE}}] determines the half duration of the source time function for the movie simulations.

@@

\begin{itemize}
\item the simulation type control parameters: \texttt{SIMULATION\_TYPE}
and \texttt{SAVE\_FORWARD}
\item the time step parameters \texttt{NSTEP} and \texttt{DT}
\item the absorbing boundary control parameter \texttt{ABSORBING\_CONDITIONS} on condition that the\\
  \texttt{ABSORB\_INSTEAD\_OF\_FREE\_SURFACE} flag remains unmodified after running the databases generation.
\item the movie control parameters \texttt{MOVIE\_SURFACE}, \texttt{MOVIE\_VOLUME},
and \texttt{NTSTEPS\_BETWEEN\_FRAMES}
\item the ShakeMap\textregistered option \texttt{CREATE\_SHAKEMAP}
\item the output information parameters \texttt{NTSTEP\_BETWEEN\_OUTPUT\_INFO}
and \texttt{NTSTEP\_BETWEEN\_OUTPUT\_}~\\
\texttt{SEISMOS}
\item the \texttt{PRINT\_SOURCE\_TIME\_FUNCTION} flags
\end{itemize}
Any other change to the \texttt{Par\_file} implies rerunning both
the database generator \texttt{xgenerate\_databases} and the solver \texttt{xspecfem3D}.

@@

To make a surface or volume movie of the simulation, set parameters
\texttt{MOVIE\_SURFACE}, \texttt{MOVIE\_VOLUME}, and \texttt{NTSTEP\_BETWEEN\_FRAMES}
in the \texttt{Par\_file}. Turning on the movie flags, in particular
\texttt{MOVIE\_VOLUME}, produces large output files. \texttt{MOVIE\_VOLUME}
files are saved in the \texttt{LOCAL\_PATH} directory, whereas \texttt{MOVIE\_SURFACE}
output files are saved in the \texttt{OUTPUT\_FILES} directory. We
save the displacement field if the parameter \texttt{SAVE\_DISPLACEMENT} is set, otherwise the velocity field is saved.
The look of a movie is determined by the
half-duration of the source. The half-duration should be large enough
so that the movie does not contain frequencies that are not resolved
by the mesh, i.e., it should not contain numerical noise. This can
be accomplished by selecting a CMT \texttt{HALF\_DURATION} > 1.1 $\times$
smallest period (see figure \ref{fig:CMTSOLUTION-file}). When \texttt{MOVIE\_SURFACE}
= .\texttt{true.}, the half duration of each source in the \texttt{CMTSOLUTION}
file is replaced by

@@

When running \texttt{xspecfem3D} with the \texttt{MOVIE\_SURFACE}
flag turned on, the code outputs \texttt{moviedata??????} files in
the \texttt{OUTPUT\_FILES} directory. There are several flags
in the main parameter file \texttt{Par\_file} that control the output of these moviedata files
(see section \ref{cha:Main-Parameter} for details):
\texttt{\small NTSTEP\_BETWEEN\_FRAMES} to set the timesteps between frames,
\texttt{\small SAVE\_DISPLACEMENT} to save displacement instead of velocity,
\texttt{USE\_HIGHRES\_FOR\_MOVIES} to save values at all GLL point instead of element edges.
In order to output additionally shakemaps, you would set
the parameter \texttt{CREATE\_SHAKEMAP} to \texttt{.true.}.

>>>>

\item [{\texttt{OLSEN\_ATTENUATION\_RATIO}}] Determines the Olsen's constant in Olsen's empirical relation (see \citet{OlDaBr03}).

@@

\item [{\texttt{MOVIE\_TYPE}}] Set this flag to 1 to show the top
  surface (tomography + oceans) only, to 2 to show all external faces
  of the mesh (i.e. topography + vertical edges + bottom) in shakemaps and surface movies.

@@

\item [{\texttt{HDUR\_MOVIE}}] Determines the half duration of the source time function for the movie simulations.

@@

\begin{itemize}
\item the simulation type control parameters: \texttt{SIMULATION\_TYPE}
and \texttt{SAVE\_FORWARD}
\item the time step parameters \texttt{NSTEP} and \texttt{DT}
\item the absorbing boundary control parameter \texttt{ABSORBING\_CONDITIONS} on condition that the\\
  \texttt{ABSORB\_INSTEAD\_OF\_FREE\_SURFACE} flag remains unmodified after running the databases generation.
\item the movie control parameters \texttt{MOVIE\_SURFACE}, \texttt{MOVIE\_VOLUME},
and \texttt{NTSTEPS\_BETWEEN\_FRAMES}
\item the ShakeMap\textregistered option \texttt{CREATE\_SHAKEMAP}
\item the output information parameters \texttt{MOVIE\_TYPE}, \texttt{NTSTEP\_BETWEEN\_OUTPUT\_INFO}
and \texttt{NTSTEP\_BETWEEN\_OUTPUT\_}~\\
\texttt{SEISMOS}
\item the \texttt{PRINT\_SOURCE\_TIME\_FUNCTION} flags
\end{itemize}
Any other change to the \texttt{Par\_file} implies rerunning both
the database generator \texttt{xgenerate\_databases} and the solver \texttt{xspecfem3D}.

@@

To make a surface or volume movie of the simulation, set parameters
\texttt{MOVIE\_SURFACE}, \texttt{MOVIE\_VOLUME}, \texttt{MOVIE\_TYPE}, and \texttt{NTSTEP\_BETWEEN\_FRAMES}
in the \texttt{Par\_file}. Turning on the movie flags, in particular
\texttt{MOVIE\_VOLUME}, produces large output files. \texttt{MOVIE\_VOLUME}
files are saved in the \texttt{LOCAL\_PATH} directory, whereas \texttt{MOVIE\_SURFACE}
output files are saved in the \texttt{OUTPUT\_FILES} directory. We
save the displacement field if the parameter \texttt{SAVE\_DISPLACEMENT} is set, otherwise the velocity field is saved.
The look of a movie is determined by the
half-duration of the source. The half-duration should be large enough
so that the movie does not contain frequencies that are not resolved
by the mesh, i.e., it should not contain numerical noise. This can
be accomplished by selecting a CMT \texttt{HALF\_DURATION} > 1.1 $\times$
smallest period (see figure \ref{fig:CMTSOLUTION-file}). When \texttt{MOVIE\_SURFACE}
= .\texttt{true.}, the half duration of each source in the \texttt{CMTSOLUTION}
file is replaced by

@@

When running \texttt{xspecfem3D} with the \texttt{MOVIE\_SURFACE}
flag turned on, the code outputs \texttt{moviedata??????} files in
the \texttt{OUTPUT\_FILES} directory. There are several flags
in the main parameter file \texttt{Par\_file} that control the output of these movie data files
(see section \ref{cha:Main-Parameter} for details):
\texttt{\small NTSTEP\_BETWEEN\_FRAMES} to set the timesteps between frames,
\texttt{\small SAVE\_DISPLACEMENT} to save displacement instead of velocity,
\texttt{USE\_HIGHRES\_FOR\_MOVIES} to save values at all GLL point instead of element edges.
In order to output additionally shakemaps, you would set
the parameter \texttt{CREATE\_SHAKEMAP} to \texttt{.true.}.
